---
title: "milestone_3"
author: "Ryan Graff"
date: "October 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lintr)
library(gt)
library(glue)
library(knitr)
library(styler)
library(readxl)
library(janitor)
library(ggplot2)
library(rvest)
library(tidyverse)
```

```{r data import, include=FALSE, echo=FALSE}
# Importing and naming raw data
draft_18 <- "https://www.basketball-reference.com/draft/NBA_2018.html#stats::none"
# Reading raw data and naming said data.  I am now ready to start working with the data
draft <- read_html(draft_18)

# x <- html_node(x = draft, xpath = test_node_xpath)
```

# I have data! (I am just struggling to import it)

https://www.basketball-reference.com/draft/NBA_2018.html

https://www.basketball-reference.com/draft/NBA_2017.html

https://www.basketball-reference.com/draft/NBA_2016.html

https://www.basketball-reference.com/draft/NBA_2015.html

https://www.basketball-reference.com/draft/NBA_2014.html

https://www.basketball-reference.com/draft/NBA_2013.html

etc.

This data comes from basketball-reference.com.  I have done nothing with it yet as it is proving very difficult to import.  This data includes draft position and career stats.

I will also be seeking data from https://stats.nba.com/ in order to get data on all current NBA players.

Additional data may come from fivethirtyeight, as I believe they have some advanced basketball performance measures that I want to investigate and potentially incorporate.



# So what am I going to do with it all?

Basically, once I pull in all this data, I want to start determining the expected career worth of an NBA draft pick in various metrics (Points Per Game, VORP, Win Shares, more tbd), and then be able to compare draft picks to each other as well as to existing NBA players (For example, how many first round picks is Anthony Davis really worth? And does it matter where in the first round those picks are going to be?).  Assuming I can get all of that done, I would love to somehow incorporate a time element into the current player valuations, aka how many first rounders was Anthony Davis worth at 22 vs. now at 26, when he has less time left in his career. 



```{r}
print(draft)
```

